---
title: linear model analysis 
output: 
  html_document:
    toc: yes
    toc_float: yes
---

```{r }
rm(list = ls())
knitr::opts_chunk$set(eval = T, cache = T, message = F, warning=F)
library(dplyr)
library(magrittr)
library(ggplot2)
library("gridExtra")
library("cowplot")
library(car)
library(FactoMineR)
library(ade4)
library(vegan)
library(MASS)
library(ellipse)
path <- "C:\\Users\\emduc\\Desktop\\"
# path <- "./data/" # To be used on sylvain local machine
```

# data

```{r}
trait <- read.csv(file.path(path, "environment_trait2.csv"),header = T, dec = ".", sep=",")

topo <- read.csv(file.path(path, "topo_sympho.csv"),header = T, dec = ".", sep=";") 

topo <- topo %>% 
  dplyr::filter(TypeTopoEN !="")  

trait <- trait  %>% 
  mutate(Dawkins = as.factor(as.character(Dawkins))) %>% 
  full_join(topo) %>% 
  dplyr::select(n_parcelle, n_carre, n_arbre,SLA, LT_mean, Chloro_content, LMDC, d_creek, wetness, TypeTopoEN, Dawkins, dem, slope, TRI, aspect, curvature, d_log_gap, Competition, diameter) %>% 
  dplyr::filter(!is.na(TypeTopoEN))
```

## standardisation 

```{r}

trait_standar <- trait %>%
  dplyr::select(n_parcelle, n_carre, n_arbre,LT_mean, Chloro_content, LMDC, SLA) %>% 
  mutate(LT_mean = (LT_mean/ (mean(trait$LT_mean)))) %>% 
  mutate(Chloro_content = (Chloro_content/ (mean(trait$Chloro_content)))) %>% 
   mutate(SLA= (SLA/ (mean(trait$SLA)))) 

environment_standar <- trait %>% 
  dplyr::select(n_parcelle, n_carre, n_arbre,wetness,Competition,   d_creek, aspect, curvature, TRI, diameter,dem,slope, TypeTopoEN, Dawkins, d_log_gap) %>% 
  mutate( diameter= (diameter/ (mean(trait$diameter)))) %>% 
  mutate( d_creek= (d_creek/ (mean(trait$d_creek)))) %>%
  mutate( wetness= (wetness/(mean(trait$wetness)))) %>% 
  mutate( dem= (dem/(mean(trait$dem)))) %>% 
  mutate( slope= (slope/(mean(trait$slope)))) %>%
  mutate( TRI= (TRI/(mean(trait$TRI)))) %>%
  mutate( curvature= (curvature/(mean(trait$curvature)))) %>%
  mutate( aspect= (aspect/(mean(trait$aspect)))) %>%
  mutate( Competition= (Competition/(mean(trait$Competition)))) %>% 
mutate( d_log_gap= (d_log_gap/(mean(trait$d_log_gap))))

```

##data modification 




```{r}
panel.cor <- function(x, y, digits=2, prefix="", cex.cor) {
  usr <- par("usr")
  on.exit(par(usr))
  par(usr = c(0, 1, 0, 1))
  r <- abs(cor(x, y, use = "complete.obs"))
  txt <- format(c(r, 0.123456789), digits = digits)[1]
  txt <- paste(prefix, txt, sep = "")
  if (missing(cex.cor)) cex <- 0.8 / strwidth(txt)

  test <- cor.test(x, y)
  # borrowed from printCoefmat
  Signif <- symnum(
    test$p.value, corr = FALSE, na = FALSE,
    cutpoints = c(0, 0.05, 0.1, 1),
    symbols = c("*", ".", " ")
  )

  text(0.5, 0.5, txt, cex = cex * r)
  text(.8, .8, Signif, cex = cex, col = 2)
}
pairs(environment_standar[,4:10], lower.panel = panel.smooth, upper.panel = panel.cor)
```

A we can see on the pairs plot TRI and slope are highly correlated so we need to choose one to do not influence RDA, slope seems to be easier to interprete. Also diameter,  Competition index are really correlated, here competition bring a special information that can not be removed and diameter is in a way summarised in the competition index because it is based on the basal area that is calculated with DBH. 

```{r}
environment_standar <- environment_standar %>% 
  dplyr::select(-TRI , -diameter)

pairs(environment_standar[,4:10], lower.panel = panel.smooth, upper.panel = panel.cor)
```


Then I need to choose between dem, slope and wetness as the wetness index is derivated from dem and other topographic information like slope so all the information is summarised in wetness.

```{r}
environment_standar <- environment_standar %>% 
  dplyr::select(-slope, -dem)

pairs(environment_standar[,4:11], lower.panel = panel.smooth, upper.panel = panel.cor)
```
SO now there is a hudge correlation between d_log_gap and d_creek due to bottom land is not exploitable so logging gap had been done with a certain distance from those area. D_creek give a better ecological information, than d_log_gap because exploitation had been done sevral years ago and do not longer impact leaf functionnal trait due to the reduce leaf life span. 

Wetness and type topo are correlated and as wetness is a derivative analysis of topographic information it would be better to choose it because topographic information is preserve.

Finally Dawkins to competition don't know, it would be better with d_gap because without Dawkins wa lost light information that cannot be extract from competition even if they are correlated. 

```{r}
environment_standar <- environment_standar %>% 
  dplyr::select(-d_log_gap, -TypeTopoEN, -Dawkins)

pairs(environment_standar[,4:8], lower.panel = panel.smooth, upper.panel = panel.cor)
```


```{r}
library(faraway)
sort(vif(environment_standar) )
```

Borcard et al. 2011: 175 argue that in the case of RDA, VIFs > 10 should be avoided, so here everything is right. 





#rda 
## analysis

If lm part is not run before you need to remove n_parcelle, n_carre and n_arbre from trait_standar and environment_standar

```{r}
 trait_standar2 <- trait_standar %>% 
  dplyr::select(-n_parcelle, -n_carre, -n_arbre)
environment_standar2 <- environment_standar %>% 
  dplyr::select(-n_parcelle, -n_carre, -n_arbre)

rda_trait <- rda(trait_standar2~.,environment_standar2,scale = T, na.omit= T)
summary(rda_trait)

```

Now rda model validation 
```{r}
coef(rda_trait)
set.seed(111)
anova.cca(rda_trait, step=1000)
anova.cca(rda_trait, by="axis", step= 1000)
```

rda result plot

```{r}
plot(rda_trait, scaling = 0.5, main = "Triplot RDA scaling 1 - wa scores")
var.sc <- scores(rda_trait, choices = 1:2, scaling = 1, display = "sp")
arrows(0, 0, var.sc[, 1], var.sc[, 2], length = 0, lty = 1, col = "red")
```



# lm 

Using standardized data and only uncorrelated data to avoid singularities error in multiplicative model 
```{r}
data_standar <- full_join(environment_standar,trait_standar) %>%
  
  dplyr::select(-n_parcelle, -n_carre, -n_arbre) 

data_standar$Dawkins <- trait$Dawkins
```


## SLA

### step both


```{r}
# trait <- trait %>% 
#   dplyr::select(-n_parcelle, -n_carre, -n_arbre)
# 
# SLA_model <-  lm(SLA~., data= trait)
# step(object = SLA_model, direction = "both")

# lm(formula = SLA ~ LT_mean + Chloro_content + LMDC + d_creek + 
#     Dawkins + d_log_gap, data = trait) %>% summary() #both 

SLA_model <-  lm(SLA~., data= data_standar)
#step(object = SLA_model, direction = "both")

lm(formula = SLA ~ d_creek + LT_mean + Chloro_content + LMDC + 
    Dawkins, data = data_standar) %>% summary

lm(formula = SLA ~ d_creek * Dawkins  * LT_mean +
    Chloro_content * LMDC, data = data_standar) %>% summary
```


here multiplicative model with the same pre-selected variables from step have a better adjusted Rsquarred than the additive one respectiveky 0.7152 and 0.7066 butI don't think that the difference is really significant. 

### step forward

```{r}
step(object = SLA_model, direction = "forward")
lm(formula = SLA ~ LT_mean + Chloro_content + LMDC + d_creek + 
    wetness + TypeTopoEN + Dawkins + dem + slope + TRI + aspect + 
    curvature + d_log_gap, data = trait) %>% summary # forward
```
 The forwar analysis seems to do some mistake when we summarize the call formula.. 

### step backward

```{r}
step(object = SLA_model, direction = "backward")
lm(formula = SLA ~ LT_mean + Chloro_content + LMDC + d_creek + 
    Dawkins + d_log_gap, data = trait) %>%  summary# backward
```

with the backwar analysis we have the same result than "both" step method. th adjusted R-squared is 0.7086 , a quite good value 


## LMDC
### step both

```{r}
 data_standar2<- data_standar %>%
  dplyr::select(-SLA) 
  
LMDC_model <- lm(LMDC~., data=data_standar2)
step(object = LMDC_model, direction = "both")

lm(formula = LMDC ~ wetness + Competition + curvature + Chloro_content + 
    Dawkins, data = data_standar2) %>%  summary()

 lm(formula = LMDC ~ Competition *wetness * Chloro_content* Dawkins, data = data_standar2 ) %>%  summary()
```
here with the selected variable from step put in an multiplicative model there is no significant interaction and the adjusted R-squared is  0.3344 whereas with the additive model the adjusted R-squared is  0.3612. So as there is no significant interaction the additive model will be selected. 

### step backwar

```{r}
step(object = LMDC_model, direction = "backward")

lm(formula = LMDC ~ Chloro_content + d_creek + Dawkins + dem + 
    TRI + curvature + d_log_gap + Competition, data = data_standar2) %>% summary()
```

### step forward


```{r}
step(object = LMDC_model, direction = "forward")

lm(formula = LMDC ~ LT_mean + Chloro_content + d_creek + wetness + 
    TypeTopoEN + Dawkins + dem + slope + TRI + aspect + curvature + 
    d_log_gap + Competition + diameter, data = data_standar2) %>% summary()
```

Backward method is better Adjusted R-squared:  0.3919 

## LT
### step both


```{r}
LT_mean_model <- lm(LT_mean~., data=data_standar2)
step(object = LT_mean_model, direction = "both")

lm(formula = LT_mean ~ wetness + Competition + curvature + Dawkins, 
    data = data_standar2) %>%  summary()

 lm(formula = LT_mean ~ wetness * 
     Dawkins * Dawkins* Competition , data = data_standar2) %>%  summary()
```
the multiplicative form does not show any interesting interaction between variable and have a smaller adjusted R-squared : 0.2582 against 0.267
### step backward
```{r}
step(object = LT_mean_model, direction = "backward")

lm(formula = LT_mean ~ wetness + diameter + dem + TypeTopoEN + 
    Dawkins + Chloro_content, data = data_standar2) %>% summary()
```

### step forward

```{r}
step(object = LT_mean_model, direction = "forward")

lm(formula = LT_mean ~ wetness + Competition + d_creek + aspect + 
    curvature + TRI + diameter + dem + slope + TypeTopoEN + Dawkins + 
    d_log_gap + Chloro_content + LMDC, data = data_standar2)%>% summary()
```

Once again forward method does not work well and result from both method is the same than the backward one. And Adjusted R-squared:  0.3322 



## chloro content
using data standar with SLA value because chlorocontent is not correlated or a component of SLA

### step both

```{r}

Chloro_content_model <- lm(Chloro_content~., data=data_standar)
step(object = Chloro_content_model, direction = "both")

lm(formula = Chloro_content ~ wetness + Competition + aspect + 
    LT_mean + LMDC + SLA, data = data_standar) %>%  summary()

 lm(formula = Chloro_content ~ Competition * aspect *  LMDC * SLA+ LT_mean, data = data_standar) %>%  summary()

```
aspect is selected by step function but it is not significant when lm is applied alone ..

Multiplicative form give almost the same adjusted R-squared but there are just a few significant variables and interactions. 
### step backward
```{r}
step(object = Chloro_content_model, direction = "backward")

lm(formula = Chloro_content ~ Competition + aspect + diameter + 
    dem + LMDC + SLA, data = data_standar) %>% summary()
```
Same result as both direction 

### step forward

```{r}
step(object = Chloro_content_model, direction = "forward")

lm(formula = Chloro_content ~ wetness + Competition + d_creek + 
    aspect + curvature + TRI + diameter + dem + slope + TypeTopoEN + 
    Dawkins + d_log_gap + LT_mean + LMDC + SLA, data = data_standar)%>% summary()
```

Once again forward method does not work well and result from both method is the same than the backward one. And Adjusted R-squared:  0.3176


