---
title: "LT model"
output: html_document
---
# option 
```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list = ls())

library(dplyr)
library(ggplot2)
library(car)

path <- "C:\\Users\\emduc\\Desktop\\Drive\\symphostage\\"
```

```{r}
data_standar <- read.csv(file.path(path, "data_standar.csv"),header = T, dec = ".", sep=",") %>%  mutate(Dawkins = as.factor(Dawkins))
```
#model  

So leaves would be thicker (so Lth would be highter) in sunnier, dryer and less fertile habitats as well as longer-lived leaves. (pérez, 2013)

So wetness , d_creek should influence thickness value as they are proxy of soil water avalaibility. As we previously saw with SLA diameter and it interaction with d_gap, lBAL and aspect with their respective interaction with diamter can influence light availaibility. 

```{r}
LT_model <- lm(LT_mean~  Dawkins + wetness + lBAL + d_creek  + diameter + ombrage+
 d_gap + lBAL:diameter+ d_gap:diameter + diameter:wetness + diameter:d_creek , data=data_standar[,4:15])

summary(LT_model)

AIC(LT_model)
```



```{r}
LT_model <- lm(LT_mean~ Dawkins +wetness + lBAL + d_creek  + diameter +
 diameter:lBAL , data=data_standar)

summary(LT_model)

AIC(LT_model)
```

Coefficient : 
  - Wetness : coeffcient is positive so as expected leaf thickness increased when wetness value increased which mean that the soil water availability decreased (wetness decreased)
  - lBAL : negative coefficient when crowding is hight leaf thickness descred... don't know what to say about that 
  - d_creek : as expected and same as wetness highter is the distance between the focal tree and the creek thicker are the leaves. Generally when the distance with the creek is hight soil water availaibility descreased. 
  -diameter : bigger is the tree diameter thicker are the leaves. It make sense younger tree are under layer canopy and so that light availability is lower than in the canopy. So big diameter means hight tree and so individuals that already have reach the canopy and their leaves are thicker due to an hight exposition to sun.
  - diameter:lBAL, negative coefficient so the impact of diameter decreased when lBAL decreased. So Leaves would thinner when lBAL value is low. 
  


```{r}
par(mfrow = c(2,2))
plot(LT_model)
```
# step 


```{r}
step_data <- data_standar %>%  dplyr::select(-X, -n_parcelle, -n_carre, -n_arbre, -SLA, -LMDC, -Area_exclude, -Chloro_content)

#LT_full <- lm(formula = LT_mean ~., data = step_data)

#step(LT_full, data = step_data , direction = "backward")
        
```

```{r}
summary(lm(formula = LT_mean ~ Dawkins + wetness + lBAL + d_creek + diameter, 
    data = step_data)) 

```

