---
title: plot data
output: 
  html_document:
    toc: yes
    toc_float: yes
---

```{r doc settings,  package, message=FALSE, warning=FALSE}
rm(list = ls())
knitr::opts_chunk$set(eval = T, cache = T, message = F, warning=F)
library(dplyr)
library(magrittr)
library(ggplot2)
library(ggpubr)
library("gridExtra")
library("cowplot")
library(FactoMineR)
library(factoextra)
```

# data upload
 
```{r}
path <- "C:\\Users\\emduc\\Desktop\\Drive\\symphostage\\"
# path <- "./data/" # To be used on sylvain local machine
Traits_brut_data <- read.csv(file.path(path, "Full_traits_data.csv"),header = T, dec = ",", sep=";")
```

Transform mean individuals data because we are looking for inter-individual variation and not intra-individual only for numeric variables here 

```{r}
Trait_mean_individuals_num <- Traits_brut_data %>% 
  group_by(n_parcelle, n_carre, n_arbre) %>% 
  summarize_at(c("Area_exclude", "Area_include", "Fresh_weight", "Dry_Weight", "SPAD_mean", "LT_mean", "Branch_diameter", "Bark_thickness", "Bark_infra_density", "Wood_infra_density" ), mean, na.rm = T)
```

And here for non numeric information like Dawkins and morphotype

```{r }
Traits_brut_data <- Traits_brut_data %>% 
  rename(wood_presence = Bois) %>% 
  mutate(wood_presence = as.factor(wood_presence))

Trait_mean_individuals_vect<- Traits_brut_data %>% 
  dplyr::select(n_parcelle, n_carre, n_arbre, morphotype, Dawkins, diameter, Xutm, Yutm, wood_presence, morphotype_field) %>% 
  group_by(n_parcelle, n_carre, n_arbre, morphotype, Dawkins, diameter, wood_presence, morphotype_field) %>%
    summarize()

#write.csv(Trait_mean_individuals_vect, file = "C:\\Users\\emduc\\Desktop\\coord_sympho.csv" )
```



# transformed trait 

We are going to add transformed trait to our data table like Leaf Dry Mass Content (LMDC), Specific Leaf Area (SLA) and Chorophyll content from SPAD

```{r}
Trait_mean_transform <- Trait_mean_individuals_num %>% 
  mutate(SLA = Area_exclude / Dry_Weight) %>% 
  mutate(LMDC = Dry_Weight/ Fresh_weight) %>% 
  mutate(Chloro_content = ((154.1* SPAD_mean)/(197.6-SPAD_mean))) %>% 
  select(n_parcelle, n_carre, n_arbre, "LT_mean", "Branch_diameter", "Bark_thickness", "Bark_infra_density", "Wood_infra_density", LMDC, SLA, Chloro_content)
```


chlorophyll content transformation come from Coste et al 2010 but with parameters from papers and not re-fitted with our data .. 
And now merging trait mean num and vect to have an complete mean trait value table 

```{r }
Trait_mean_transform_final <- merge(Trait_mean_transform, Trait_mean_individuals_vect, by = c("n_parcelle", "n_carre", "n_arbre") ) %>%
  mutate(Dawkins = gsub("A","",Dawkins)) %>% 
  mutate(Dawkins = gsub("B","",Dawkins)) %>% 
  mutate(Dawkins = gsub("C","",Dawkins)) %>% 
  mutate(Dawkins = as.factor(as.integer(Dawkins))) %>% 
  filter( SLA < 200) %>% 
  filter(Dawkins != "") %>% 
  mutate( basal_area = (pi* (diameter)^2)/4)

#write.csv2(Trait_mean_transform_final , "C:\\Users\\emduc\\Desktop\\Drive\\symphostage\\Full_traits_transform.csv")

```

# environment data
## environment fromparacou SIG 
```{r}
environment <-read.csv(file.path(path, "environment\\Paracou\\environmenttest.csv"),header = T, dec = ",", sep=";")%>% 
  select(-morphotype, -X, -circonf, -espece, -n_essence, -Famille, -Genre, -code_vivant, -code_mesure, -idTaxon, -campagne, -X.1)


environment_trait <- Trait_mean_transform_final %>%  inner_join(environment, by = c("n_parcelle", "n_carre", "n_arbre"))
```

merging environmental data with transformed trait data, only 398 are in commun so one individual is missing lets found which one 

```{r}
Trait_mean_transform_final %>% anti_join(environment_trait , by= c("n_parcelle", "n_carre", "n_arbre"))

```

So 14-2-459 is present in environment data base 

## environment from neighbour basal area 

```{r}
G_neighbour <- read.csv(file.path(path, "Full_Gneighbour.csv"),header = T, dec = ".", sep=",")

G_neighbour <- G_neighbour %>% 
  select(PointWeight, nNeighbors, GNeighbors, n_parcelle, n_carre, n_arbre )

environment_trait2 <- G_neighbour %>% 
  inner_join(environment_trait, by = c("n_parcelle", "n_carre", "n_arbre"))

#write.csv(environment_trait2, file = "C:\\Users\\emduc\\Desktop\\environment_trait2.csv" )

Trait_mean_transform%>%  anti_join(environment_trait2, by = c("n_parcelle", "n_carre", "n_arbre"))

```
So here 4 individuals are missing from the full corrected  individual count data because there is a filter on indvidual with aberrant SLA >200 (11-1-742 : 842 and 11-4-983 : 489) , individual without Dawkins value ( 15-1-198) and the last one that is missing from environmental data (14-2-459).

### competition index 

```{r}
environment_trait2 <- environment_trait2 %>% 
  mutate(Competition = ((GNeighbors/ nNeighbors)/PointWeight))

#write.csv(environment_trait2, file = "C:\\Users\\emduc\\Desktop\\environment_trait2.csv" )
```

### dcm 

```{r}
dcm <- read.csv(file.path(path, "sympho_dcm.csv"),header = T, dec = ".", sep=",")

environment_trait2 <- dcm %>% 
  select(-X) %>% 
  inner_join(environment_trait2, by = c("n_parcelle", "n_carre", "n_arbre"))

```


# plot 
## simple trait 
### SLA distribution 

```{r}
 Trait_mean_transform_final %>%    
ggplot( aes(SLA))+
  geom_histogram(na.rm= T, binwidth = 4)
```

There are two individuals that have aberrant SLA value 11-1-742 : 842 and 11-4-983 : 489 

### LMDC distribution 

```{r}
ggplot(Trait_mean_transform_final, aes(LMDC))+
  geom_histogram(binwidth = 0.008)
```



  
### LT distribution 

```{r}
ggplot(Trait_mean_transform_final, aes(LT_mean))+
  geom_histogram(na.rm = T, binwidth = 12)
```

### Chlorophylle content distribution 

```{r}
ggplot(Trait_mean_transform_final, aes(Chloro_content))+
  geom_histogram(na.rm = T, binwidth = 2)
```

## double trait 
### SLA ~ LMDC

```{r }
Trait_mean_transform_final %>%   
ggplot(aes(SLA, LMDC, color= morphotype, size = diameter))+
  geom_jitter(na.rm=T)+
  labs(title = "", y="Leaf Dry Matter Content (LMDC) in g", x="Specific leaf area (SLA)")
```


```{r }
Trait_mean_transform_final %>% 
ggplot(aes(SLA, LMDC))+
  geom_density2d(na.rm=T )+
  background_grid(major = "xy", minor = "none")
```


```{r }
P_sp.1 <- Trait_mean_transform_final %>% 
  filter(morphotype == "sp.1") %>% 
ggplot(aes(SLA, LMDC))+
  geom_density2d()+
  background_grid(major = "xy", minor = "none")+
   labs(title = "sp.1")

P_globu <- Trait_mean_transform_final %>% 
  filter(morphotype == "globulifera") %>% 
ggplot(aes(SLA, LMDC))+
  geom_density2d()+
  background_grid(major = "xy", minor = "none")+
   labs(title = "globulifera")

P_indet <- Trait_mean_transform_final %>% 
  filter(morphotype == "Indet.") %>% 
ggplot(aes(SLA, LMDC))+
  geom_density2d()+
  background_grid(major = "xy", minor = "none")+
   labs(title = "indet")

P_sp.1_indent <- Trait_mean_transform_final %>% 
  filter(morphotype != "globulifera") %>% 
ggplot(aes(SLA, LMDC))+
  geom_density2d()+
  background_grid(major = "xy", minor = "none")+
   labs(title = "sp.1 et indet")

plot_grid(P_sp.1, P_globu, P_indet, P_sp.1_indent   , labels=c("A", "B","C", "D"), ncol = 2, nrow = 2)
```




```{r }
Trait_mean_transform_final %>% 
ggplot(aes(SLA, LMDC))+
  geom_density2d(na.rm=T )+
  background_grid(major = "xy", minor = "none")
```


```{r }
P_sp.1 <- Trait_mean_transform_final %>% 
  filter(morphotype_field == "S") %>% 
ggplot(aes(SLA, LMDC))+
  geom_density2d()+
  background_grid(major = "xy", minor = "none")+
   labs(title = "S")

P_globu <- Trait_mean_transform_final %>% 
  filter(morphotype_field == "G") %>% 
ggplot(aes(SLA, LMDC))+
  geom_density2d()+
  background_grid(major = "xy", minor = "none")+
   labs(title = "G")

P_indet <- Trait_mean_transform_final %>% 
  filter(morphotype_field == "SG") %>% 
ggplot(aes(SLA, LMDC))+
  geom_density2d()+
  background_grid(major = "xy", minor = "none")+
   labs(title = "SG")

P_sp.1_indent <- Trait_mean_transform_final %>% 
  filter(morphotype_field != "G") %>% 
ggplot(aes(SLA, LMDC))+
  geom_density2d()+
  background_grid(major = "xy", minor = "none")+
   labs(title = "S et SG")

plot_grid(P_sp.1, P_globu, P_indet, P_sp.1_indent   , labels=c("A", "B","C", "D"), ncol = 2, nrow = 2)
```

### LMDC ~ LT 

```{r}
ggplot(Trait_mean_transform_final, aes(LT_mean, LMDC, color= morphotype, size = diameter))+
  geom_jitter(na.rm=T)
```

```{r }
ggplot(Trait_mean_transform_final,aes(LT_mean, LMDC))+
  geom_density2d(na.rm=T, col = "orange")
```
```{r }
P_sp.1 <- Trait_mean_transform_final %>% 
  filter(morphotype == "sp.1") %>% 
ggplot(aes(LT_mean, LMDC))+
  geom_density2d()+
  background_grid(major = "xy", minor = "none")+
   labs(title = "sp.1")

P_globu <- Trait_mean_transform_final %>% 
  filter(morphotype == "globulifera") %>% 
ggplot(aes(LT_mean, LMDC))+
  geom_density2d()+
  background_grid(major = "xy", minor = "none")+
   labs(title = "globulifera")

P_indet <- Trait_mean_transform_final %>% 
  filter(morphotype == "Indet.") %>% 
ggplot(aes(LT_mean, LMDC))+
  geom_density2d()+
  background_grid(major = "xy", minor = "none")+
   labs(title = "Indet")

P_sp.1_indent <- Trait_mean_transform_final %>% 
  filter(morphotype != "globulifera") %>% 
ggplot(aes(LT_mean, LMDC))+
  geom_density2d()+
  background_grid(major = "xy", minor = "none")+
   labs(title = "sp.1 et indet")

plot_grid(P_sp.1, P_globu, P_indet, P_sp.1_indent   , labels=c("A", "B","C", "D"), ncol = 2, nrow = 2)
```

### SLA ~ LT 

```{r}
Trait_mean_transform_final %>%  filter(SLA < 200) %>% 
ggplot( aes(LT_mean, SLA, color= morphotype, size = diameter))+
  geom_jitter(na.rm=T)
```

```{r }
ggplot(Trait_mean_transform_final,aes(LT_mean ,SLA))+
  geom_density2d(na.rm=T, col = "orange")
```

```{r }
P_sp.1 <- Trait_mean_transform_final %>% 
  filter(morphotype == "sp.1") %>% 
ggplot(aes(SLA, LT_mean))+
  geom_density2d()+
  background_grid(major = "xy", minor = "none")+
   labs(title = "sp.1")

P_globu <- Trait_mean_transform_final %>% 
  filter(morphotype == "globulifera") %>% 
ggplot(aes(SLA, LT_mean))+
  geom_density2d()+
  background_grid(major = "xy", minor = "none")+
   labs(title = "globulifera")

P_indet <- Trait_mean_transform_final %>% 
  filter(morphotype == "Indet.") %>% 
ggplot(aes(SLA, LT_mean))+
  geom_density2d()+
  background_grid(major = "xy", minor = "none")+
   labs(title = "Indet")

P_sp.1_indent <- Trait_mean_transform_final %>% 
  filter(morphotype != "globulifera") %>% 
ggplot(aes(SLA, LT_mean))+
  geom_density2d()+
  background_grid(major = "xy", minor = "none")+
   labs(title = "sp.1 et indet")

plot_grid(P_sp.1, P_globu, P_indet, P_sp.1_indent   , labels=c("A", "B","C", "D"), ncol = 2, nrow = 2)
```

### Chlorophylle content ~ SLA 

```{r}
Trait_mean_transform_final %>%  filter(SLA < 200) %>% 
ggplot( aes(SLA, Chloro_content, color= morphotype, size = diameter))+
  geom_jitter(na.rm=T)
```

```{r }
ggplot(Trait_mean_transform_final,aes(SLA,Chloro_content))+
  geom_density2d(na.rm=T, col = "orange")
```



```{r }
P_sp.1 <- Trait_mean_transform_final %>% 
  filter(morphotype == "sp.1") %>% 
ggplot(aes(SLA, Chloro_content))+
  geom_density2d()+
  background_grid(major = "xy", minor = "none")+
   labs(title = "sp.1")

P_globu <- Trait_mean_transform_final %>% 
  filter(morphotype == "globulifera") %>% 
ggplot(aes(SLA, Chloro_content))+
  geom_density2d()+
  background_grid(major = "xy", minor = "none")+
   labs(title = "globulifera")

P_indet <- Trait_mean_transform_final %>% 
  filter(morphotype == "Indet.") %>% 
ggplot(aes(SLA, Chloro_content))+
  geom_density2d()+
  background_grid(major = "xy", minor = "none")+
   labs(title = "Indet")

P_sp.1_indent <- Trait_mean_transform_final %>% 
  filter(morphotype != "globulifera") %>% 
ggplot(aes(SLA, Chloro_content))+
  geom_density2d()+
  background_grid(major = "xy", minor = "none")+
   labs(title = "sp.1 et indet")

plot_grid(P_sp.1, P_globu, P_indet, P_sp.1_indent   , labels=c("A", "B","C", "D"), ncol = 2, nrow = 2)
```

### Chlorophylle content ~ LMDC


```{r}
ggplot(Trait_mean_transform_final , aes(LMDC, Chloro_content, color= morphotype, size = diameter))+
  geom_jitter(na.rm=T)
```

```{r }
ggplot(Trait_mean_transform_final,aes(LMDC,Chloro_content))+
  geom_density2d(na.rm=T, col = "orange")
```

```{r }
P_sp.1 <- Trait_mean_transform_final %>% 
  filter(morphotype == "sp.1") %>% 
ggplot(aes(LMDC, Chloro_content))+
  geom_density2d()+
  background_grid(major = "xy", minor = "none")+
   labs(title = "sp.1")

P_globu <- Trait_mean_transform_final %>% 
  filter(morphotype == "globulifera") %>% 
ggplot(aes(LMDC, Chloro_content))+
  geom_density2d()+
  background_grid(major = "xy", minor = "none")+
   labs(title = "globulifera")

P_indet <- Trait_mean_transform_final %>% 
  filter(morphotype == "Indet.") %>% 
ggplot(aes(LMDC, Chloro_content))+
  geom_density2d()+
  background_grid(major = "xy", minor = "none")+
   labs(title = "Indet")

P_sp.1_indent <- Trait_mean_transform_final %>% 
  filter(morphotype != "globulifera") %>% 
ggplot(aes(LMDC, Chloro_content))+
  geom_density2d()+
  background_grid(major = "xy", minor = "none")+
   labs(title = "sp.1 et indet")

plot_grid(P_sp.1, P_globu, P_indet, P_sp.1_indent   , labels=c("A", "B","C", "D"), ncol = 2, nrow = 2)
```


### Chlorophylle content ~ LT


```{r}

ggplot(Trait_mean_transform_final  ,aes(LT_mean, Chloro_content, color= morphotype, size = diameter))+
  geom_jitter(na.rm=T)
```

```{r }
ggplot(Trait_mean_transform_final,aes(LT_mean,Chloro_content))+
  geom_density2d(na.rm=T, col = "orange")
```

```{r }
P_sp.1 <- Trait_mean_transform_final %>% 
  filter(morphotype == "sp.1") %>% 
ggplot(aes(LT_mean, Chloro_content))+
  geom_density2d()+
  background_grid(major = "xy", minor = "none")+
   labs(title = "sp.1")

P_globu <- Trait_mean_transform_final %>% 
  filter(morphotype == "globulifera") %>% 
ggplot(aes(LT_mean, Chloro_content))+
  geom_density2d()+
  background_grid(major = "xy", minor = "none")+
   labs(title = "globulifera")

P_indet <- Trait_mean_transform_final %>% 
  filter(morphotype == "Indet.") %>% 
ggplot(aes(LT_mean, Chloro_content))+
  geom_density2d()+
  background_grid(major = "xy", minor = "none")+
   labs(title = "Indet")

P_sp.1_indent <- Trait_mean_transform_final %>% 
  filter(morphotype != "globulifera") %>% 
ggplot(aes(LT_mean, Chloro_content))+
  geom_density2d()+
  background_grid(major = "xy", minor = "none")+
   labs(title = "sp.1 et indet")

plot_grid(P_sp.1, P_globu, P_indet, P_sp.1_indent   , labels=c("A", "B","C", "D"), ncol = 2, nrow = 2)
```

### Wood density ~ bark density
```{r}
Trait_mean_transform_final %>%  
ggplot( aes(Wood_infra_density, Bark_infra_density, color= morphotype, size = diameter))+
  geom_jitter(na.rm=T)
```

## Trait and environment 
### SLA ~ Dawkins 
```{r}
Trait_mean_transform_final %>%   
ggplot( aes(x = diameter, y = SLA, color= Dawkins))+
  geom_point()
```
there is one individuals without Dawkins evaluation that have been removed at the begining.

We can see that there is a logical correlation between Dawkins and diameter so this subjective evaluation is quite good (developp why "logical") . Then smaller is the Dawkins score highter is the SLA value. It is not suprising because SLA reflect the leaf acquisition capacity and for individuals under the canopy light is less evalable so having hight SLA value allow to intercept more light and so maximise growth in adverse conditions (Long et al 2011).

```{r}
Trait_mean_transform_final %>% 
ggplot( aes(x = Dawkins, y =SLA , fill = Dawkins))+
  geom_boxplot()+
   stat_compare_means(method = "anova", 
                     label.y = 250) +
  stat_compare_means(method = "t.test", 
                     label = "p.signif",
                     ref.group = ".all.",
                     label.y = 225)
  

```
 
```{r}
Trait_mean_transform_final %>% 
  aov(SLA ~ Dawkins, data=.) %>% 
  TukeyHSD()
```

```{r }
P_sp.1 <- Trait_mean_transform_final %>% 
  filter(morphotype == "sp.1") %>% 
ggplot(aes(SLA, diameter))+
  geom_density2d()+
  background_grid(major = "xy", minor = "none")+
   labs(title = "sp.1")

P_globu <- Trait_mean_transform_final %>% 
  filter(morphotype == "globulifera") %>% 
ggplot(aes(SLA, diameter))+
  geom_density2d()+
  background_grid(major = "xy", minor = "none")+
   labs(title = "globulifera")

P_indet <- Trait_mean_transform_final %>% 
  filter(morphotype == "Indet.") %>% 
ggplot(aes(SLA, diameter))+
  geom_density2d()+
  background_grid(major = "xy", minor = "none")+
   labs(title = "Indet")

P_sp.1_indent <- Trait_mean_transform_final %>% 
  filter(morphotype != "globulifera") %>% 
ggplot(aes(SLA, diameter))+
  geom_density2d()+
  background_grid(major = "xy", minor = "none")+
   labs(title = "sp.1 et indet")

plot_grid(P_sp.1, P_globu, P_indet, P_sp.1_indent   , labels=c("A", "B","C", "D"), ncol = 2, nrow = 2)

```


## Branch wood presence ~ diameter 

```{r}
ggplot(Trait_mean_transform_final, aes(x= Dawkins, y= wood_presence, size = diameter, color = morphotype))+
  geom_jitter()
```
Repartition between diameter category seems to be homogene, so there is no link between branch sample and diameter. Broken branches does not come from weaker wood from older or younger individual with diameter used as a proxy for the "age".




#ACP 



```{r}
ACP_data<- environment_trait2 %>% 
  select(LMDC, SLA, Chloro_content, LT_mean, morphotype_field, diameter) 


res.pca <- PCA(ACP_data, quali.sup = 5, graph= F, scale.unit = T)

 ind <- fviz_pca_ind(res.pca, label="none", habillage=ACP_data$morphotype,
             addEllipses=TRUE, ellipse.level=0.95)
var <-  fviz_pca_var(res.pca, alpha.var="contrib")
 both <- fviz_pca_biplot(res.pca, label ="var")
 
 plot_grid(ind, var, both  , labels=c("A", "B","C"), ncol = 2, nrow = 2)

```

That a bit surprising because when SLA and LMDC are plotted together it seems to related but here they are not so much .. And this is the same for LT ... 

So Chlorophyll content can be reduce to LMDC and LT by diameter ? 

"Missing values are imputed by the mean of the variable: you should use the imputePCA function of the missMDA package" so wood and bark data are not input here 


## diameter ~ LT
```{r}
Trait_mean_transform_final %>%  
ggplot(aes(LT_mean,diameter, color= morphotype))+
  geom_jitter(na.rm=T)
```

 
Within individuals, many studies have shown that outer-canopy ‘sun’ leaves tend to be thicker than those from more-shaded parts of the canopy. So thickness is related to light availability and as we previously saw diameter is positively related to Dawkins and therefore to individual light availibity. So this is not suprising that bigger is the diameter, thicker leaves are gonna be. 

## SLA ~diameter 

```{r}
Trait_mean_transform_final %>%   
ggplot(aes(diameter, LT_mean, color= morphotype))+
  geom_jitter(na.rm=T)
```
## ACP environment 
### topographic variables 
```{r}
ACP_data2<- environment_trait2 %>% 
  select( dem,  slope, morphotype_field) 
  


res.pca2 <- PCA(ACP_data2, quali.sup = 3, graph = F)

ind2 <- fviz_pca_ind(res.pca2, label="none", habillage = ACP_data2$morphotype_field,
             addEllipses=TRUE, ellipse.level=0.95)
 
# var2 <-  
var12 <-  fviz_pca_var(res.pca2,axes = c(1, 2), alpha.var="contrib")
# var23 <-  fviz_pca_var(res.pca2,axes = c(3, 2), alpha.var="contrib")
# var13 <-  fviz_pca_var(res.pca2,axes = c(1, 3), alpha.var="contrib")

both2 <- fviz_pca_biplot(res.pca2, axes = c(1, 2), label ="var", habillage = ACP_data2$morphotype_field)

plot_grid(var12, var23, var13, both2, ncol = 2, nrow = 2)
```

TRI and slope are highly correlated not so surprising because TRI depict topographic microheterogeneity and calculted with difference of elevation between raster cells and currently land elevation imply slope. 

choose between TRI and slope 

Now for curvature variable that depict the changes in slope, I am not sure that it bring any ecological information in our case change in slope would be summarised in wetness index. 

Does aspect is used in wetness index definition ? 

Aspect : the aspect of each raster cell (here 1m²)grouped into compass direction (north; north-west etc)

### soil variables 

```{r eval = F}
load("C:\\Users\\emduc\\Desktop\\Drive\\symphostage\\soil_data.Rdata")

ACP_data4<- soil_nutrient %>% 
  select( MO, C_N, CEC, ) 
  
res.pca4 <- PCA(ACP_data4, graph = F)

 
var12 <-  fviz_pca_var(res.pca4,axes = c(1, 2), alpha.var="contrib")
var23 <-  fviz_pca_var(res.pca4,axes = c(3, 2), alpha.var="contrib")
var13 <-  fviz_pca_var(res.pca4,axes = c(1, 3), alpha.var="contrib")


plot_grid(var12, var23, var13, ncol = 2, nrow = 2)

nutriment <- soil_nutrient %>% 
  select( MO, C_N, CEC, Plot) %>% 
  rename(n_parcelle = Plot) %>% 
  group_by(n_parcelle) %>% 
  summarize_all(mean)
```

(Refus, MO, C, N, C_N, Polsen, PBray2, Al_KCl, Mg_ech, K_ech, Na_ech, S, CEC, TS)


### water variable 

waterlog, hydromorphy = discrete variables not continuous 

```{r}
ACP_data5<- environment_trait2 %>% 
  select( wetness,  slope, dem, Competition, morphotype_field) 

res.pca5 <- PCA(ACP_data5, quali.sup = 5, graph = F)
 
var12 <-  fviz_pca_var(res.pca5,axes = c(1, 2), alpha.var="contrib")
var23 <-  fviz_pca_var(res.pca5,axes = c(3, 2), alpha.var="contrib")
var13 <-  fviz_pca_var(res.pca5,axes = c(1, 3), alpha.var="contrib")

plot_grid(var12, var23, var13, ncol = 2, nrow = 2)

both12 <- fviz_pca_biplot(res.pca5, axes = c(1, 2), label ="var",habillage = ACP_data5$morphotype_field)
both23 <- fviz_pca_biplot(res.pca5, axes = c(3, 2), label ="var")
both13 <- fviz_pca_biplot(res.pca5, axes = c(3, 1), label ="var")
```




## ACP trait and environment
ACP without : aspect, d_logging_gap , d_creek 
```{r}

ACP_data3<- environment_trait2 %>% 
  select(wetness, dem, slope, LMDC, SLA ,LT_mean ,Competition, morphotype_field) 


res.pca3 <- PCA(ACP_data3, graph= F, quali.sup = 8)
#plot.PCA(res.pca3, axes=c(3, 2), choix="var", habillage=13)
#choix="ind"

var12 <-  fviz_pca_var(res.pca3,axes = c(1, 2), alpha.var="contrib")
var23 <-  fviz_pca_var(res.pca3,axes = c(3, 2), alpha.var="contrib")
var13 <-  fviz_pca_var(res.pca3,axes = c(1, 3), alpha.var="contrib")

plot_grid(var12, var23, var13, ncol = 2, nrow = 2)

both12 <- fviz_pca_biplot(res.pca3, axes = c(1, 2), label ="var" ,habillage = ACP_data3$morphotype_field)
both23 <- fviz_pca_biplot(res.pca3, axes = c(3, 2), label ="var",habillage = ACP_data3$morphotype_field)
both13 <- fviz_pca_biplot(res.pca3, axes = c(3, 1), label ="var")

plot_grid(both12, both23, both13, ncol = 2, nrow = 2)

```
## test ACP avec vegan

ACP whith scale = T, to work with covariance matrix because data have different unite (so data are not centered) then using scaling = 1 and scaling = 2 to maintain euclidian distance or correlation between descriptor (verified whichone is use by factomineR)
```{r}
# library(vegan)
# 
# ACP_data3 %<>% 
#   select(-morphotype, -waterlog) 
# 
# ACP=rda(ACP_data3,scale=TRUE)
# truc1 <- biplot(ACP,scaling=1)
# truc2 <- biplot(ACP,scaling=2)
#  plot_grid(truc1, truc2 , labels=c("A", "B"), ncol = 2, nrow = 1)

```

